\section{Transfer matrix analysis of ring resonator cavities}
\label{ringResAppen}
A useful way to describe the spectral response of a ring resonator is by defining a transfer matrix. This $2\times2$ matrix relates the electric fields of the inputs and outputs of the waveguide and resonator. In our analysis we define the electric fields to be complex valued and also normalised to conserve energy, this condition implies the transfer matrix must be unitary.

First write down the obvious relations

% Equation for E_out
\begin{equation}
E_{out}=r_1E_{in}+t_1E_2
\end{equation}

%Equation for E_1
\begin{equation}
E_{1}=r_2E_2+t_2E_{in}
\end{equation}

Define a matrix.
\begin{equation}
M = \begin{pmatrix}
r_1 & t_1 \\
t_2 & r_2 \\
\end{pmatrix}
\end{equation}
Enforce unitarity
\begin{equation}
\begin{pmatrix}
r_1 & t_1 \\
t_2 & r_2 \\
\end{pmatrix}
\begin{pmatrix}
r^*_1 & t^*_2 \\
t^*_1 & r^*_2 \\
\end{pmatrix}
=
\begin{pmatrix}
|r_1|^2+|t_1|^2 & r_1t^*_2+r^*_2t_1 \\
r_2t^*_1+r^*_1t_2 & |r_2|^2+|t_2|^2 \\
\end{pmatrix}=
\begin{pmatrix}
1 & 0 \\
0 & 1 \\
\end{pmatrix}
\end{equation}
Furthermore $\det{M}=1$
\begin{equation}
r_1r_2-t_1t_2=1
\end{equation}
so 
\begin{equation}
r_2=\frac{1+t_1t_2}{r_1}
\end{equation}
Also $M^{-1}=M^*$
\begin{equation}
\begin{pmatrix}
r_2 & -t_1 \\
-t_2 & r_1 \\
\end{pmatrix}=
\begin{pmatrix}
r^*_1 & t^*_1 \\
t^*_2 & r^*_2 \\
\end{pmatrix}
\end{equation}
This tells us $r_1$ and $r_2$ must be real.
So we can simplify the unitarity equation. 
So
\begin{equation}
t_1=iT_1
\end{equation}
\begin{equation}
t_2=iT_2
\end{equation}
Rewrite the interesting equations:
Use also $r_2=r^*_1$
\begin{equation}
\begin{pmatrix}
|r_1|^2+T_1^2 & -ir_1T_2+ir_1T_1 \\
-ir^*_1T_1+ir^*_1T_2 & |r_1|^2+T_2^2 \\
\end{pmatrix}=
\begin{pmatrix}
1 & 0 \\
0 & 1 \\
\end{pmatrix}
\end{equation}
Ok so $T_2=T_1=t$
\begin{equation}
\begin{pmatrix}
|r_1|^2+t^2 & 0 \\
0 & |r_1|^2+t^2 \\
\end{pmatrix}=
\begin{pmatrix}
1 & 0 \\
0 & 1 \\
\end{pmatrix}
\end{equation}
\begin{equation}
|r_1|^2=1-t^2
\end{equation}
\begin{equation}
|r_2|^2=1-t^2
\end{equation}d
Basically I have a degree of freedom. $r_1=e^{i\theta}r$ and $r_2=e^{-i\theta}r$. Choose $\theta = 0$ for simplicity.

Now the matrix is:
\begin{equation}
\begin{pmatrix}
r & it \\
it & r \\
\end{pmatrix}
\end{equation}

Now we add that $$E_2=\tau e^{i\theta}E_1$$

Recall the initial equations.
% Equation for E_out
\begin{equation}
E_{out}=rE_{in}+itE_2
\end{equation}
%Equation for E_1
\begin{equation}
E_{1}=rE_2+itE_{in}
\end{equation}
%Equation for E_1
\begin{equation}
E_{1}=r\tau e^{i\theta}E_1+itE_{in}
\end{equation}
%
\begin{equation}
\frac{E_{1}}{E_{0}}=\frac{it}{1-r\tau e^{i\theta}}
\end{equation}
Okay so thats $E_1$ done.
\begin{equation}
\frac{E_{1}}{E_{0}}=\frac{it}{1-r\tau e^{i\theta}}
\end{equation}
\begin{equation}
\left|\frac{E_{1}}{E_{0}}\right |^2=\frac{t^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
For $E_{2}$ we have:
\begin{equation}
\frac{E_{2}}{E_{0}}=\frac{it\tau e^{i\theta}}{1-r\tau e^{i\theta}}
\end{equation}
%
\begin{equation}
\left |\frac{E_{2}}{E_{0}}\right |^2=\frac{\tau^2-\tau^2r^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
For $E_{out}$ we have:
\begin{equation}
\frac{E_{out}}{E_{0}}=r+it\frac{it\tau e^{i\theta}}{1-r\tau e^{i\theta}}
\end{equation}
\begin{equation}
\frac{E_{out}}{E_{0}}=\frac{r-r^2\tau e^{i\theta}-t^2\tau e^{i\theta}}{1-r\tau e^{i\theta}}
\end{equation}
%abs val
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{(r-r^2\tau e^{i\theta}-t^2\tau e^{i\theta})(r-r^2\tau e^{-i\theta}-t^2\tau e^{-i\theta})}{(1-r\tau e^{i\theta})(1-r\tau e^{-i\theta})}
\end{equation}
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{(r(r-r^2\tau e^{-i\theta}-t^2\tau e^{-i\theta})-r^2\tau e^{i\theta}(r-r^2\tau e^{-i\theta}-t^2\tau e^{-i\theta})-t^2\tau e^{i\theta}(r-r^2\tau e^{-i\theta}-t^2\tau e^{-i\theta}))}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
%
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{r^2-r^3\tau e^{-i\theta}-rt^2\tau e^{-i\theta}-r^3\tau e^{i\theta}+r^4\tau^2+2r^2\tau^2t^2-rt^2\tau e^{i\theta}+t^4\tau^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
%
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{r^2-e^{-i\theta}(r^3\tau+rt^2\tau)-e^{i\theta}(r^3\tau+rt^2\tau)+r^4\tau^2+t^4\tau^2+2r^2\tau^2t^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
%
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{r^2+2(r^3\tau+rt^2\tau)\cos(\theta)+r^4\tau^2+t^4\tau^2+2r^2\tau^2t^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
%
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{r^22(r^3\tau+r(1-r^2)\tau)\cos(\theta)+r^4\tau^2+(1-r^2)^2\tau^2+2r^2\tau^2(1-r^2)}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
%
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{r^2-2(r^3\tau+r(1-r^2)\tau)\cos(\theta)+r^4\tau^2+(1-2r^2+r^4)\tau^2+2r^2\tau^2-2r^4\tau^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
%
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{r^2-2r\tau\cos(\theta)+r^4\tau^2+\tau^2-2r^2\tau^2+r^4\tau^2+2r^2\tau^2-2r^4\tau^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
%
\bf{FINAL RESULTS}
\begin{equation}
\left |\frac{E_{out}}{E_{0}}\right|^2=\frac{r^2-2r\tau\cos(\theta)+\tau^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}
\begin{equation}
\left |\frac{E_{2}}{E_{0}}\right |^2=\frac{\tau^2-\tau^2r^2}{1+r^2\tau^2-2r\tau cos(\theta)}=\tau^2\left|\frac{E_{1}}{E_{0}}\right |^2
\end{equation}
\begin{equation}
\left|\frac{E_{1}}{E_{0}}\right |^2=\frac{t^2}{1+r^2\tau^2-2r\tau cos(\theta)}
\end{equation}